Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-13 analysis/paper/sim_survey_paper.Rmd
Add figure captions

Ideally the parameter settings used here would be based on model fits to real data, however, conditioning the operating model described above was outside the scope of this project. Moreover, many of the parameters described above may not be identifiable or it may be difficult to obtain un-biased estimates [e.g. bias introduced by length-stratified sampling complicate the fitting of growth models; @Morgan1997]. As such, parameters were informally selected to roughly correspond to observations typically obtained by the Fisheries and Oceans Canada survey of cod in NAFO division 3Ps, Newfoundland. Though this approach is far from exact, the goal was to approximate the life-history and distribution of an actual population to simulate an arena for testing the consequences of surveys with different sampling protocol. Parameter settings and descriptions used in this case study are presented in Table \@ref(tab:par). A series of `r nrow(sim$surveys)` surveys were tested using an array of different sampling protocol outlined in Table \@ref(tab:tests). Each survey was simulated `r max(sim$age_strat_error$sim)` times over the same population and samples were run through a stratified analysis [@Smith1981] to obtain an estimate of abundance at age for each year for each simulation, $\hat{I}_{a,y,k}$. We used root-mean-squared error (RMSE) as a measure of the percision and bias of the abundance estimates from each survey:

@@

@@

Table: (\#tab:par) Parameter descriptions, symbols and global settings used in the cod case study.

@@

Table: (\#tab:tests) Descriptions and settings of different survey sampling protocol tested in the cod case study. All possible combinations of the options below were tested.

@@

```{r ex_fig, fig.height = 3.8, fig.width = 8.5}

@@

```{r est_fig, fig.height = 9, fig.width = 8.5}

@@

```{r error_fig, fig.height = 3, fig.width = 8.5, results = "hide"}

>>>>

Ideally the parameter settings used here would be based on model fits to real data, however, conditioning the operating model described above was outside the scope of this project. Moreover, many of the parameters described above may not be identifiable or it may be difficult to obtain un-biased estimates [e.g. bias introduced by length-stratified sampling complicate the fitting of growth models; @Morgan1997]. As such, parameters were informally selected to roughly correspond to observations typically obtained by the Fisheries and Oceans Canada survey of cod in NAFO division 3Ps, Newfoundland. Though this approach is far from exact, the goal was to approximate the life-history and distribution of an actual population to simulate an arena for testing the consequences of surveys with different sampling protocol. Parameter settings and descriptions used in this case study are presented in Table \@ref(tab:par). A series of `r nrow(sim$surveys)` surveys were tested using an array of different sampling protocol outlined in Table \@ref(tab:tests). Each survey was simulated `r max(sim$age_strat_error$sim)` times over the same population and samples were run through a stratified analysis [@Smith1981] to obtain an estimate of abundance at age for each year for each simulation, $\hat{I}_{a,y,k}$. We used root-mean-squared error (RMSE) as a measure of the precision and bias of the abundance estimates from each survey:

@@

\@ref(fig:sp-fig)

@@

Table: (\#tab:par) - Parameter descriptions, symbols and global settings used in the cod case study.

@@

Table: (\#tab:tests) - Descriptions and settings of different survey sampling protocol tested in the cod case study. All possible combinations of the options below were tested.

@@

```{r sp-fig, cache = TRUE, fig.height = 3.8, fig.width = 8.5, fig.cap = "- An example from year seven of the simulation of a) the distribution of total abundance available to the survey, and b) locations of the sets conducted and total numbers caught in a stratified random survey with a set density of 0.002 sets / km^2^."}

@@

```{r est-fit, cache = TRUE, fig.height = 9, fig.width = 8.5, fig.cap = "- Stratified estimates of abundance at age across years from 10 simulations of a survey with a set density of 0.002 sets / km^2^ and sampling caps of 500 lengths per set and 10 ages per length group. The heavy dark line indicates the true tred in the population available to the survey."}

@@

```{r error-fig, cache = TRUE, fig.height = 3, fig.width = 8.5, results = "hide", fig.cap = "- Wireframe plot of root-mean-squared error (RMSE) from an array of surveys with different sampling protocol. Panels represent surveys with different set densities ($D_{sets}$), x-axes represnet the maximum sampling effort of lengths per set ($M_{lengths}$), and y-axes represent the maximum number of ages to collect per length group ($M_{ages}$)"}
